% A B S T R A C T
% ---------------

\begin{center}\textbf{Abstract}\end{center}


The purpose of this project is to present a framework for controlling operations of Internet of Things (IoT) devices operating in a building environment, for instance.  Motivated by the open source software architecture developed under the Department of Energy called the Building Energy Management Open Source Software (BEMOSS), the current project aims at controlling IoT devices using the proposed BEMOSS framework. The existing BEMOSS framework has the ability to automate building operations using a particular set of supported IoT devices, such as heating, ventilating, and air conditioning (HVAC) controllers, lighting, load devices, and sensors. Here, we propose to generalize this idea by controlling the operation of a new IoT device that the existing BEMOSS framework does not recognize.  The new IoT device considered in this work is a brushed permanent magnet DC motor that is expected to be operated using the proposed BEMOSS framework. BEMOSS is installed on server machine running Linux operating system. A hardware interfacing circuit has been designed and implemented for the DC motor to be recognized by the BEMOSS. A prototype of the operating principle of the proposed BEMOSS framework running a new IoT device (i.e., DC motor) will be presented to demonstrate its performance. Furthermore, an HVAC control algorithm developed to be integrated into the proposed BEMOSS framework. 



% This paper presents a method for controlling multiple Internet of Things (IoT) devices. This work uses an open source software from Virginia Tech called Building Energy Management Open Source Software (BEMOSS) to connect multiple IoT devices to one server. This server is run on a linux laptop and manage a variety of IoT devices. This papers work allows the use of BEMOSS on a Raspberry Pi, a cheap commercially available microcontroller, to run commands through BEMOSS. Currently BEMOSS supports a number of commercial IoT devices and in this work, a new device, a DC motor, has been implemented to be run on BEMOSS. Lastly a heating, ventilating, and air conditioning (HVAC) control algorithm has been implemented to be later introduced onto BEMOSS. 

\cleardoublepage
%\newpage




%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReport"
%%% End:
